\chapter{Project Progress\label{ch:project_progress}}

This chapter documents the progress of the project throughout the three
sprints (alpha, beta and final version). Each sprint had a pre\-pen\-ded
planning phase, in which the sprint targets were discussed and potentially
adjusted. This procedure goes along well with the Agile Manifesto which
encourages the design of a complex system in small incremental parts.

The detailed process, as well as the planned targets and actual
results for each sprint, are mentioned in the sections below.

\section{Sprint 1: Alpha Version}

The planned features for the first sprint were:
\begin{itemize}
	\item RDS demodulation
	\item PSK31 demodulation
	\item Logging the output of digital demodulators (Morse, RDS and PSK31)
\end{itemize}

Unfortunately, there were several unforseen tasks that had to be treated
before the new features could actually be implemented. These are:
\begin{itemize}
	\item The migration to Android Studio
	\item Necessary memory management optimizations
	\item Refactoring tasks on the Morse \ac{GUI}
	\item Bugfix: Broken scanner mode when using the \emph{HackRF}
\end{itemize}

Therefore, the PSK31 demodulation had to be postponed to sprint two. The
logging feature was deferred to the last sprint, when both RDS and
PSK31 are finished.


\section{Sprint 2: Beta Version}

Because of the exam phase, the feature set for sprint two was consciously
kept small and the transmission-related features were pushed to sprint
three. The features planned for the second sprint were:
\begin{itemize}
	\item RDS demodulation optimizations
	\item PSK31 demodulation
	\item Morse demodulation (refactoring)
	\item SDRplay support
\end{itemize}

Additionally to the planned features, a bugfix to fix the
broken recording feature of \ac{AnSiAn} was implemented, which helped in developing the
PSK31 demodulation algorithm.

\section{Sprint 3: Final Version}

The final sprint included the remaining mandatory features:
\begin{itemize}
	\item rad1o support
	\item Logging the output of digital demodulators (Morse, RDS and PSK31)
	\item Transmission
		\begin{itemize}
			\item Raw IQ file
			\item Morse transmission
		\end{itemize}
\end{itemize}

Also, many \ac{GUI} fixes and cleanups were included into the final version
as well as an additional PSK31 transmission feature and a finalized
Morse demodulation algorithm.

